### 2024-03-17 content/chapter_1.tex
:pencil: Add programmable metamaterials

\begin{section}{Motivation}
	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
	However, the desire of human and machine for better communication shows no signs of slowing down.
	Emerging applications such as smart cities, autonomous driving, telemedicine, extended reality, federated learning, and generative intelligence are calling for a stronger and smarter wireless infrastructure.
	It is envisioned that 6G will be designed to meet the following requirements \cite{Tataria2021,Alsabah2021,Jiang2021}:
	\begin{itemize}
		\item \emph{Throughput}: The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
		\item \emph{Latency}: Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
		\item \emph{Reliability}: A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
		\item \emph{Connectivity}: The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
		\item \emph{Coverage}: Poor coverage has been another bottleneck for 5G. A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment. Privacy can be enhanced with federated learning and homomorphic encryption.
		% \item \emph{Superintelligent}: The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
	\end{itemize}

@@

\begin{section}{Overview on \glsfmtfull{ris}}

>>>>

\begin{section}{Motivation}
	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
	However, the desire of human and machine for better communication shows no signs of slowing down.
	Emerging applications such as smart cities, autonomous driving, telemedicine, extended reality, federated learning, and generative intelligence are calling for a stronger and smarter wireless infrastructure.
	It is envisioned that 6G will be designed to meet the following requirements \cite{Tataria2021,Alsabah2021,Jiang2021}:
	\begin{itemize}
		\item \emph{Throughput:} The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
		\item \emph{Latency:} Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
		\item \emph{Reliability:} A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
		\item \emph{Connectivity:} The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
		\item \emph{Mobility:} Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
		\item \emph{Energy efficiency:} Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
		\item \emph{Positioning accuracy:} Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
		\item \emph{Coverage:} Poor coverage has been another bottleneck for 5G. A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
		\item \emph{Security and privacy:} Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment. Privacy can be enhanced with federated learning and homomorphic encryption.
		% \item \emph{Superintelligent:} The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
	\end{itemize}

@@

\begin{section}{Overview on \glsfmtfull{ris}}\label{sc:ris_overview}

### 2024-03-17 content/chapter_2.tex
:pencil: Add programmable metamaterials

\begin{section}{\glsfmtfull{ris}}
	\begin{subsection}{Programmable Metamaterials}
		Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
		The concept was initially proposed by Victor Veselago in 1967, who conjectured the existence of mediums with negative dielectric constant $\epsilon < 0$ and negative permeability $\mu < 0$ \cite{Veselago1968}.
		Such metamaterials are known as ``negative-index'' because the refraction index is defined as the \emph{negative} square root $n = - \sqrt{\epsilon \mu} < 0$, in order to be consistent with Maxwell's equations.
		It was not until 1999 that their feasibility was experimentally demonstrated by John Pendry at Imperial College using split-ring resonators \cite{Pendry1999}.
		Since then, metamaterials have attracted significant interests due to their counterintuitive properties, to name a few:
		\begin{itemize}
			\item \emph{Negative refraction:} As shown in Fig. \ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis. This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
			\begin{equation}
				\frac{\sin \theta_1}{\sin \theta_2} = n.
			\end{equation}
			\begin{figure}[H]
				\centering
				\subfloat[Negative Index Material\label{fg:nim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_refraction.tex}
					}
				}
				\subfloat[Positive Index Material\label{fg:pim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/pim_refraction.tex}
					}
				}
				\caption{Refraction in negative and positive index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
			\end{figure}
			\item \emph{Opposite wave direction:} As shown in Fig. \ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material. This can be inferred from the electric field equation
			\begin{equation}
				\vec{E} = \vec{E}_0 \exp(\jmath k z - \jmath \omega t)
			\end{equation}
			where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space electric field and wavenumber reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
			Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
			\begin{figure}[H]
				\centering
				\resizebox{0.5\columnwidth}{!}{
					\input{assets/chapter_2/nim_flows.tex}
				}
				\caption{Wave and energy have opposite directions in a negative-index material.}
				\label{fg:nim_flows}
			\end{figure}

		\end{itemize}

		% TODO Programmable
		\begin{figure}[H]
			\centering
			\subfloat[Incident Wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected Wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Incident and reflected waves in a programmable metamaterial.}
		\end{figure}
	\end{subsection}

>>>>

\begin{section}{\glsfmtfull{ris}}
	\begin{subsection}{Programmable Metamaterials}
		Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
		The concept was initially proposed by Victor Veselago in 1967, who conjectured the existence of mediums with negative dielectric constant $\epsilon < 0$ and negative permeability $\mu < 0$ \cite{Veselago1968}.
		Such metamaterials are known as ``negative-index'' because the refraction index is defined as the \emph{negative} square root $n = - \sqrt{\epsilon \mu} < 0$, in order to be consistent with Maxwell's equations.
		It was not until 1999 that their feasibility was experimentally demonstrated by John Pendry at Imperial College using split-ring resonators \cite{Pendry1999}.
		Since then, metamaterials have attracted significant interests due to their counterintuitive properties, to name a few:
		\begin{itemize}
			\item \emph{Negative refraction:} As shown in Fig. \ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis \cite{Veselago1968}. This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
			\begin{equation}
				\frac{\sin \theta_1}{\sin \theta_2} = n.
			\end{equation}
			It is worth mentioning that a generalized law of refraction and refraction has been proposed in \cite{Yu2011}, which has become a standard reference for the design and analysis of metamaterials.
			\begin{figure}[H]
				\centering
				\subfloat[Negative-Index Material\label{fg:nim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_refraction.tex}
					}
				}
				\subfloat[Positive-Index Material\label{fg:pim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/pim_refraction.tex}
					}
				}
				\caption{Refraction in negative and positive-index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
			\end{figure}
			\item \emph{Opposite wave direction:} As shown in Fig. \ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material \cite{Pendry2004}. This can be inferred from the electric field equation
			\begin{equation}
				\vec{E} = \vec{E}_0 \exp(\jmath k z - \jmath \omega t)
			\end{equation}
			where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space electric field and wavenumber reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
			Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
			\begin{figure}[H]
				\centering
				\subfloat[Negative-Index Material\label{fg:nim_flows}]{
					\resizebox{!}{2cm}{
							\input{assets/chapter_2/nim_flows.tex}
					}
				}
				\subfloat[Positive-Index Material\label{fg:pim_flows}]{
					\resizebox{!}{2cm}{
						\input{assets/chapter_2/pim_flows.tex}
					}
				}
				\caption{Wave and energy have opposite directions in a negative-index material.}
			\end{figure}
		\end{itemize}

		Conventional metamaterials have fixed properties that depend on the geometry and arrangement of their constituent elements.
		Once fabricated, these properties cannot be easily changed unless the structure is physically altered.
		This limits their early usage to military and defense, with applications such as invisibility cloaks and optical illusions.
		In 2014, the concept of ``coding'' and ``programmable'' metamaterials was validated by researchers at Southeast University \cite{Cui2014}, who realized digital control of radar cross-section using biased diodes and \gls{fpga}.
		With a proper model of the target properties and external citation, the metamaterial can be reconfigured in real-time for desired behaviors.
		For example, a self-adaptive metasurface equipped with motion and light sensors have been developed in \cite{Ma2019} for single- and multi-beam steering.

		Next, we discuss the principles of electromagnetic wave redirection via refraction and reflection:
		\begin{itemize}
			\item \emph{Refraction:} As shown in Fig. \ref{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}. This could be helpful for wireless applications where the transmitter and receiver are at different sides of the material.
			\item \emph{Reflection:} As shown in Fig. \ref{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}. This could be helpful for wireless applications where the transmitter and receiver are at the same side of the material.
		\end{itemize}
		% electromagnetic wave refraction and reflection.

		\begin{figure}[H]
			\centering
			\subfloat[Negative-Index Material\label{fg:nim_focus}]{
				\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_focus.tex}
				}
			}
			\subfloat[Positive-Index Material\label{fg:pim_diverge}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/chapter_2/pim_diverge.tex}
				}
			}
			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point.}
		\end{figure}
		\begin{figure}[H]
			\centering
			\subfloat[Incident Wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected Wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Reflection through metamaterials. Yellow dots represent scattering elements. Solid and dashed lines denote wavefronts and rays, respectively. The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
		\end{figure}
		It is worth noticing that refraction and reflection can be regarded as different forms of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
		In the next subsection, we will some typical \gls{ris} scattering models and their assumptions.
	\end{subsection}
